Left-linear rewriting in adhesive categories

### 2024-04-25 concur/fusione.tex
switches

The second lemma captures the essence of the consistency of
switchings. It shows that if we have a derivation consisting of three
rewriting steps, say $\dder{D}_0\cdot \dder{D}_1\cdot  \dder{D}_2$ and we switch them leading to the
sequence $\dder{D}_2\cdot  \dder{D}_1\cdot  \dder{D}_0$, we obtain the same resulting derivation,
independently from the order of the switchings.

@@

>>>>

The second lemma captures the essence of the consistency of
switchings. It shows that if we have a derivation consisting of three
rewriting steps, say $\dder{D}_0\cdot \dder{D}_1\cdot  \dder{D}_2$ and we switch them leading to a
sequence reordered as $\dder{D}_2\cdot  \dder{D}_1\cdot  \dder{D}_0$, we obtain the same resulting derivation,
independently from the order of the switchings.

@@

\todo{P: Qui si potrebbe fare lo stesso cambiamento del lemma precedente, usando

    $\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2 \shift{(0,1)}
    \dder{D}_1' \cdot \dder{D}_0' \cdot \dder{D}_2 \shift{(1,2)}
    \dder{D}_1' \cdot \dder{D}_2' \cdot \dder{D}_0''\shift{(0,1)}
    \dder{D}_2'' \cdot \dder{D}_1'' \cdot \dder{D}_0''$

$\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2 \shift{(1,2)}
    \dder{D}_0 \cdot \dder{E}_2' \cdot \dder{E}_1' \shift{(0,1)}
    \dder{E}_2'' \cdot \dder{E}_0' \cdot \dder{E}_1' \shift{(1,2)}
    \dder{E}_2'' \cdot \dder{E}_1'' \cdot \dder{E}_0''
    $
    ma credo che il dover usare $E$ renda meno facile la lettura}
